---
title: "Assignment 1"
execute:
  echo: true
  warning: false
  message: false
format: html
---

## Selected Video

**Video Title:** Veri Bilimi ve Endüstri Mühendisliği Üzerine Sohbetler - Kerem Demirtaş & Erdi Dasdemir

## Brief Summary

In this video, the speakers discuss the relationship between data science and industrial engineering. They explain that industrial engineers are increasingly expected to work with data, develop analytical thinking skills, and use programming tools to solve real-world problems.

The discussion also emphasizes that data science is not only about coding. It also requires understanding the business problem, interpreting the results correctly, and communicating insights clearly. The video highlights the importance of combining technical knowledge with practical decision-making skills.

## Open-Ended Question

**Question:**\
Why is data science becoming increasingly important for industrial engineers?

**Answer:**\
Data science is becoming more important for industrial engineers because many industrial problems now require data-driven decision making. Engineers need to analyze data, improve systems, optimize processes, and support better decisions using quantitative evidence.

## Multiple-Choice Question

**Question:**\
Which of the following is emphasized in the video as an important part of data science?

A. Only writing code\
B. Statistical thinking and problem solving\
C. Graphic design\
D. Learning foreign languages only

**Correct Answer:**\
**B. Statistical thinking and problem solving**

## Data Analysis with R

### Load the dataset

```{r}
library(dslabs)
data("polls_us_election_2016")
data <- polls_us_election_2016
```

### Define personal variables

```{r}
my_first <- "Faruk"
my_birth_year <- 2003
```

### Calculate k

```{r}
k <- (nchar(my_first) + my_birth_year) %% 15 + 8
k
```

### Display rows from the original dataset

```{r}
if (k %% 2 == 0) {
  head(data, k)
} else {
  tail(data, k)
}
```

### Total number of NA values in the dataset

```{r}
sum(is.na(data))
```

### Number of NA values per column (top 8)

```{r}
na_per_column <- sort(colSums(is.na(data)), decreasing = TRUE)
head(na_per_column, 8)
```

### Replace missing values in a new dataset

```{r}
new_data <- data

for (col in names(new_data)) {
  if (is.numeric(new_data[[col]])) {
    new_data[[col]][is.na(new_data[[col]])] <- my_birth_year + k
  } else if (is.character(new_data[[col]]) || is.factor(new_data[[col]])) {
    new_data[[col]][is.na(new_data[[col]])] <- paste0(my_first, "_", k)
  }
}
```

### Display rows from the new dataset

```{r}
if (k %% 2 == 0) {
  head(new_data, k)
} else {
  tail(new_data, k)
}
```

### Total number of remaining NA values

```{r}
sum(is.na(new_data))
```

### Check with anyNA()

```{r}
anyNA(new_data)
```

## AI Usage

AI tools were used to help organize the assignment structure and improve the wording of the explanations.

**Prompt used:**\
"Help me organize the assignment tasks, write a simple English summary of the selected video, prepare one open-ended question and one multiple-choice question with answers, and format the required R analysis in Quarto."
